Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2021-02-03 5.URS/URS.tex
DONE!
Ready for one final pass. Specifically, in the PDF, pls look at pages:

29, 30, 60 (notation <...>) Proofs of Propositons 5.1 and 5.3, Def. 5.3.

Page 115.

There is only one UNDEFINED reference on page 115. I can fix it once I understand the context better.

In this setting, the Berman's condition, introduced in \cite{berman1964limit}, requires that
\begin{equation} \label{eq:Berman}
    r_p \log p \to 0,\ \ \mbox{ as }p\to\infty.
\end{equation}
This condition entails that 
\begin{equation}
    \label{eq:Gauss-max-in-distribution}
  a_p (M_p - b_p) \stackrel{d}{\longrightarrow } Z,\  \ \mbox{ as }p\to\infty,
\end{equation}
with the Gumbel limit distribution $\mathbb P [Z\le x] = \exp\{-e^{-x}\},\ x\in \mathbb R$, 
where 
$$
a_p = \sqrt{2\log p},\quad b_p  = \sqrt{2\log p} - \frac{1}{2}\left(\sqrt{2\log p}\right)^{-1}\left(\log \log (p) + \log(4\pi)\right),
$$ 
are {\em the same} centering and normalization sequences
as in the case of iid $\epsilon(i)$'s.  
Berman's condition is one of the weakest dependence conditions  in the literature for which this result holds. See, e.g., Theorem 4.4.8 in \cite{embrechts2013modelling}, where \eqref{eq:Berman} is described as ``very weak''.

For dependence conditions weaker than \eqref{eq:Berman}, the sequences of normalizing and centering constants in \eqref{eq:Gauss-max-in-distribution} are {\em different} from the iid case, and the corresponding limit is no longer Gumbel; see, for example, Theorems 6.5.1 and  6.6.4 in \cite{leadbetter2012extremes}, and \cite{mccormick1976weak}. 
% In particular, \cite{mccormick1976weak} derived the normalizing constants when both $r_p\to 0$ monotonically and  $r_p \log p \to \infty$ monotonically, as $p\to\infty$. 
% In this case, convergence in distribution still takes place, with the maxima concentrating along a sequence asymptotic to \eqref{eq:quantiles}.

On the other hand, in our high dimensional support estimation context, the notion of relative stability is sufficient and more natural than the finer notions of distributional convergence.
If one is merely interested in the asymptotic relative stability of the Gaussian maxima, then Berman's condition can be relaxed significantly (see also, Theorem 4.1 of \cite{berman1964limit}). 
Observe that by Proposition \ref{prop:UDD-equivalent},  the Berman condition \eqref{eq:Berman} implies UDD and hence relative stability (Theorem \ref{thm:Gaussian-weak-dependence}), i.e., 
\begin{equation} \label{eq:Gaussian-URS}
  \frac{1}{b_p} M_p \stackrel{\mathbb P}{\to} 1,\quad\mbox{as}\quad p\to\infty.
\end{equation}
This {\em concentration of maxima} property can be readily deduced from \eqref{eq:Gauss-max-in-distribution}, since $a_p b_p \sim 2\log(p) \to \infty$ as $p\to\infty$.
Theorem \ref{thm:Gaussian-weak-dependence} shows that \eqref{eq:Gaussian-URS} holds if the much weaker uniform dependence condition UDD holds. 
Note that our condition is coordinate free --- neither monotonicity of the sequence $r_p$ nor stationarity of the underlying array is required.

@@

The rest of this chapter is devoted to the proof of the main result, i.e., Theorem \ref{thm:Gaussian-weak-dependence}. 
We first introduce a key lemma regarding the structure of correlation matrix of high-dimensional random variables.
The proof uses a surprising, yet elegant application of Ramsey's Theorem from the study of combinatorics.
%; this application, and its consequences in high-dimensional probability, are presented in Section \ref{subsec:Ramsey}.
The `only if' part of Theorem \ref{thm:Gaussian-weak-dependence} follows from this lemma, in Section \ref{sec:URS=>UDD}.

The proof of the `if' part is detailed in Section \ref{sec:UDD=>URS}.
The arguments there was recently extended to establish bounds on the rate of concentration of maxima in \cite{kartsioukas2019rate}; see also, \cite{tanguy2015some} and references therein for related work on this topic.

\section{Ramsey's Coloring theorem and structure of correlation matrices} 
\label{sec:Ramsey}
\input{5.URS/5.proofs-Ramsey.tex}

\section{URS implies UDD (`only if' part of Theorem \ref{thm:Gaussian-weak-dependence})} 
\label{sec:URS=>UDD}
\input{5.URS/5.proofs-URS-UDD.tex}

\section{UDD implies URS (`if' part of Theorem \ref{thm:Gaussian-weak-dependence})} 
\label{sec:UDD=>URS}
\input{5.URS/5.proofs-UDD-URS.tex}

>>>>

In this setting, the Berman's condition, introduced in \cite{berman1964limit}, requires that
\begin{equation} \label{eq:Berman}
    r_p \log p \to 0,\ \ \mbox{ as }p\to\infty.
\end{equation}
This condition entails that 
\begin{equation}
    \label{eq:Gauss-max-in-distribution}
  a_p (M_p - b_p) \stackrel{d}{\longrightarrow } Z,\  \ \mbox{ as }p\to\infty,
\end{equation}
with the Gumbel limit distribution $\mathbb P [Z\le x] = \exp\{-e^{-x}\},\ x\in \mathbb R$, 
where 
$$
a_p = \sqrt{2\log p},\quad b_p  = \sqrt{2\log p} - \frac{1}{2}\left(\sqrt{2\log p}\right)^{-1}\left(\log \log (p) + \log(4\pi)\right),
$$ 
are {\em the same} centering and normalization sequences
as in the case of iid $\epsilon(i)$'s.  
Berman's condition is one of the weakest dependence conditions  in the literature for which the convergence in \eqref{eq:Gauss-max-in-distribution} holds. 
See, e.g., Theorem 4.4.8 in \cite{embrechts2013modelling}, where \eqref{eq:Berman} is described as ``very weak''.

Instances where the dependence in the time series is so strong that Berman's condition \eqref{eq:Berman} fails have also been studied.  In such 
cases, one may continue to have \eqref{eq:Gauss-max-in-distribution} but typically the sequences of normalizing and centering constants will be
{\em different} from the iid case, and the corresponding limit is usually no longer Gumbel; see, for example, Theorems 6.5.1 and  6.6.4 in \cite{leadbetter2012extremes}, and \cite{mccormick1976weak}. 
% In particular, \cite{mccormick1976weak} derived the normalizing constants when both $r_p\to 0$ monotonically and  $r_p \log p \to \infty$ monotonically, as $p\to\infty$. 
% In this case, convergence in distribution still takes place, with the maxima concentrating along a sequence asymptotic to \eqref{eq:quantiles}.

In our high dimensional support estimation context, the notion of relative stability is sufficient and more natural than the finer notions of distributional convergence.
If one is merely interested in the asymptotic relative stability of the Gaussian maxima, then Berman's condition can be relaxed significantly 
\citep[see also, Theorem 4.1 of][]{berman1964limit}.  Observe that by Proposition \ref{prop:UDD-equivalent},  the Berman condition \eqref{eq:Berman} implies UDD and hence relative stability (Theorem \ref{thm:Gaussian-weak-dependence}), i.e., 
\begin{equation} \label{eq:Gaussian-URS}
  \frac{1}{b_p} M_p \stackrel{\mathbb P}{\to} 1,\quad\mbox{as}\quad p\to\infty.
\end{equation}
This {\em concentration of maxima} property can be readily deduced from \eqref{eq:Gauss-max-in-distribution}, since $a_p b_p \sim 2\log(p) \to \infty$ as $p\to\infty$.
Theorem \ref{thm:Gaussian-weak-dependence} shows that \eqref{eq:Gaussian-URS} holds if the much weaker uniform dependence condition UDD holds. 
Note that our condition is coordinate free --- neither monotonicity of the sequence $r_p$ nor stationarity of the underlying array is required. This
makes it substantially broader than the time series setting in the seminal work \cite{berman1964limit}.

@@

The rest of this chapter is devoted to the proof of the main result, i.e., Theorem \ref{thm:Gaussian-weak-dependence}. 
We first introduce a key lemma regarding the structure of an {\em arbitrary} correlation matrix of high-dimensional random variables.
The proof uses a surprising, yet elegant application of Ramsey's Theorem from the study of combinatorics.
%; this application, and its consequences in high-dimensional probability, are presented in Section \ref{subsec:Ramsey}.
The `only if' part of Theorem \ref{thm:Gaussian-weak-dependence} follows from this lemma, in Section \ref{sec:URS=>UDD}.

The proof of the `if' part is detailed in Section \ref{sec:UDD=>URS}.
The arguments there have been recently extended to establish bounds on the rate of concentration of maxima in \cite{kartsioukas2019rate}; see also, \cite{tanguy2015some} and the related notion of super-concentration of \cite{chatterjee2014superconcentration}.

\section{Ramsey's  theory and the structure of correlation matrices} 
\label{sec:Ramsey}
\input{5.URS/5.proofs-Ramsey.tex}

\section{URS implies UDD (Proof of the `only if' part of Theorem \ref{thm:Gaussian-weak-dependence})} 
\label{sec:URS=>UDD}
\input{5.URS/5.proofs-URS-UDD.tex}

\section{UDD implies URS (Proof of the `if' part of Theorem \ref{thm:Gaussian-weak-dependence})} 
\label{sec:UDD=>URS}
\input{5.URS/5.proofs-UDD-URS.tex}

### 2021-02-03 6.GWAS/6.proofs-GWAS.tex
DONE!
Ready for one final pass. Specifically, in the PDF, pls look at pages:

29, 30, 60 (notation <...>) Proofs of Propositons 5.1 and 5.3, Def. 5.3.

Page 115.

There is only one UNDEFINED reference on page 115. I can fix it once I understand the context better.

On the one hand, $\text{FWER} = 1 - \P[\widehat{S}_p \subseteq S_p]$ vanishes under the Bonferroni procedure with $\alpha\to0$.
On the other hand, for large $p$, the probability of no missed detection is bounded from below by
\begin{equation} \label{eq:chi-square-sufficient-1}
    \P[\widehat{S}_p \supseteq S_p] 
    = \P[\min_{i\in S} x(i) \ge t_p] 
    \ge \P[\min_{i\in S} x(i) \ge t^*] 
    \ge 1 - p^{1-\beta}\P[\chi_\nu^2(\underline{\Delta}) < t^*],
\end{equation}
where we have used the fact that signal sizes are bounded below by $\underline{\Delta}$, and the stochastic monotonicity of chi-square distributions (Lemma \ref{lemma:stochastic-monotonicity}) in the last inequality.
Writing
$$
\chi_\nu^2(\underline{\Delta}) \stackrel{\mathrm{d}}{=} Z_1^2 + \ldots + Z_{\nu-1}^2 + (Z_\nu + \sqrt{\underline{\Delta}})^2
$$
where $Z_i$'s are iid standard normal variables, we have
\begin{align}
    \P[\chi_\nu^2({\underline{\Delta}}) < t^*]
    &\le \P[(Z_\nu+\sqrt{\underline{\Delta}})^2 < t^*] 
    = \P[|Z_\nu+\sqrt{\underline{\Delta}}| < \sqrt{t^*}]  \nonumber \\
    &\le \P\left[Z_\nu < - \sqrt{\underline{\Delta}} +  \sqrt{t^*}\right] \nonumber \\
    &= \P\left[Z_\nu < \sqrt{2\log{p}}\left(\sqrt{q} - \sqrt{\underline{r}}\right)\right]. \label{eq:chi-square-sufficient-2}
\end{align}
By our choice of $q$ in \eqref{eq:choice-of-q}, the last probability in \eqref{eq:chi-square-sufficient-2} can be bounded from above by 
\begin{align*}
    \P\Big[Z_\nu < -\sqrt{2(1-\beta)\log{p}}\Big]
    &\sim \frac{\phi\left(-\sqrt{2(1-\beta)\log{p}}\right)}{\sqrt{2(1-\beta)\log{p}}} \\
    &= \frac{1}{\sqrt{2(1-\beta)\log{p}}}p^{-(1-\beta)},
\end{align*}
where the first line uses Mill's ratio for Gaussian distributions (see Section \ref{sec:Gaussian-distributions} and Relation \eqref{eq:Mills-ratio}).
This, combined with \eqref{eq:chi-square-sufficient-1}, completes the proof of the sufficient condition for the Bonferroni's procedure.

@@

Meanwhile, for any $i\in S$, by Lemma \ref{lemma:stochastic-monotonicity} and the fact that signal sizes are bounded above by $\overline{\Delta}$, we have,
\begin{equation*}
    {\chi_\nu^2(\lambda(i))} \stackrel{\mathrm{d}}{\le}
    {\chi_\nu^2(\overline{\Delta})} \stackrel{\mathrm{d}}{=} 
    {Z_1^2 + \ldots + Z_{\nu-1}^2 + \left(Z_\nu + \sqrt{\overline{\Delta}}\right)^2}.
\end{equation*}
Dividing through by $u_p$, and taking minimum over $S$, we obtain
\begin{equation} \label{eq:chi-square-necessary-3}
    \frac{m_S}{u_p} 
    = \min_{i\in S} \frac{\chi_\nu^2(\lambda(i))}{u_p} 
    % \stackrel{\mathrm{d}}{\le} \min \left\{\frac{\chi_\nu^2(\overline{\Delta})}{u_p}, s \text{ iid copies} \right\} \\
    \stackrel{\mathrm{d}}{\le} 
    \min_{i\in S}\left\{\frac{Z_1^2(i) + \ldots + Z_{\nu-1}^2(i)}{u_p} + \frac{(Z_\nu(i) + \sqrt{\overline{\Delta}})^2}{u_p}\right\}.
\end{equation}
Let $i^\dagger = i^\dagger_p$ be the index minimizing the second term in \eqref{eq:chi-square-necessary-3}, i.e.,
\begin{equation}
    i^\dagger := \argmin_{i\in S} \frac{(Z_\nu(i) + \sqrt{\overline{\Delta}})^2}{u_p}
    = \argmin_{i\in S} f_p\left(Z_\nu(i)\right),
    % \frac{(Z_\nu(i) + \sqrt{\overline{\Delta}})^2}{2\log{p}},
\end{equation}
where $f_p(x):=(x+\sqrt{\overline{\Delta}})^2/(2\log{p})$. 
We shall first show that 
\begin{equation} \label{eq:chi-square-necessary-4}
    %\min_{i\in S} \frac{(Z_\nu(i) + \sqrt{\overline{\Delta}})^2}{2\log{p}} 
    \P[ f_p(Z_\nu(i^\dagger)) < 1 -\delta ] \to 1,
\end{equation}
for some small $\delta>0$.
On the one hand, we know (by solving a quadratic inequality) that
\begin{equation} \label{eq:chi-square-necessary-5}
    f_p(x)<1-\delta \iff \frac{x}{\sqrt{2\log{p}}} \in (-(\sqrt{\overline{r}}+\sqrt{1-\delta}), -(\sqrt{\overline{r}}-\sqrt{1-\delta})).
\end{equation}
On the other hand, we know (by relative stability of iid Gaussians \cite{gao2018fundamental}) that 
\begin{equation} \label{eq:chi-square-necessary-6}
    % f_p(\min_{i\in S}z_\nu(i)) =
    \frac{\min_{i\in S} Z_\nu(i)}{\sqrt{2\log{p}}}
    \to -\sqrt{1-\beta} \quad\text{in probability}.
\end{equation}
Further, by the assumption on the signal sizes $\overline{r} < (1+\sqrt{1-\beta})^2$, we have,
\begin{equation*}
    -(\sqrt{\overline{r}}+1) < -1 <- \sqrt{1-\beta} < - (\sqrt{\overline{r}}-1).
\end{equation*}
Therefore we can picking a small $\delta>0$ such that 
\begin{equation} \label{eq:chi-square-necessary-7}
    -(\sqrt{\overline{r}}+1) < -(\sqrt{\overline{r}}+\sqrt{1-\delta})
    < - \sqrt{1-\beta}
    < - (\sqrt{\overline{r}}-\sqrt{1-\delta})
    < - (\sqrt{\overline{r}}-1).
\end{equation}
Combining \eqref{eq:chi-square-necessary-5}, \eqref{eq:chi-square-necessary-6}, and \eqref{eq:chi-square-necessary-7}, we obtain
\begin{align*}
    \P\left[\min_{i\in S} f_p(Z_\nu(i)) < 1-\delta\right]
    &= \P\left[ f_p(Z_\nu(i^\dagger)) < 1-\delta \right] \\
    &\ge \P\left[ f_p\left(\min_{i\in S}Z_\nu(i)\right) < 1-\delta \right] \to 1,
\end{align*}
and we arrive at \eqref{eq:chi-square-necessary-4}.
As a corollary, since $u_p\sim2\log{p}$, it follows that
\begin{equation} \label{eq:chi-square-necessary-8}
    \P\left[\min_{i\in S}\frac{(Z_\nu(i) + \sqrt{\overline{\Delta}})^2}{u_p} < 1-\delta\right]\to1.
\end{equation}

@@

The proof follows the ideas in \cite{arias2017distribution}, and is very similar to the proof of Theorem \ref{thm:Gaussian-error-approx-boundary}. 
One could in principle obtain the proofs in this section by referencing arguments that have appeared in Section \ref{sec:proofs}.
We choose to present the proof here in full to make this section self-contained.

@@

As with the proof of Theorem \ref{thm:chi-squared-approx-boundary}, one could shorten the presentations in this section by referencing arguments Section \ref{sec:proofs}.
Again, we choose to present the proof in full to make this section self-contained.

>>>>

On the one hand, $\text{FWER} = 1 - \P[\widehat{S}_p \subseteq S_p]$ vanishes under the Bonferroni procedure with $\alpha\to0$.
On the other hand, for large $p$, the probability of no missed detection is bounded from below by
\begin{equation} \label{eq:chi-square-sufficient-1}
    \P[\widehat{S}_p \supseteq S_p] 
    = \P[\min_{i\in S} x(i) \ge t_p] 
    \ge \P[\min_{i\in S} x(i) \ge t^*] 
    \ge 1 - p^{1-\beta}\P[\chi_\nu^2(\underline{\Delta}) < t^*],
\end{equation}
where we have used the fact that signal sizes are bounded below by $\underline{\Delta}$, and the stochastic monotonicity of chi-square distributions (Lemma \ref{lemma:stochastic-monotonicity}) in the last inequality.
Writing
$$
\chi_\nu^2(\underline{\Delta}) \stackrel{\mathrm{d}}{=} Z_1^2 + \ldots + Z_{\nu-1}^2 + (Z_\nu + \sqrt{\underline{\Delta}})^2
$$
where $Z_i$'s are iid standard normal variables, we have
\begin{align}
    \P[\chi_\nu^2({\underline{\Delta}}) < t^*]
    &\le \P[(Z_\nu+\sqrt{\underline{\Delta}})^2 < t^*] 
    = \P[|Z_\nu+\sqrt{\underline{\Delta}}| < \sqrt{t^*}]  \nonumber \\
    &\le \P\left[Z_\nu < - \sqrt{\underline{\Delta}} +  \sqrt{t^*}\right] \nonumber \\
    &= \P\left[Z_\nu < \sqrt{2\log{p}}\left(\sqrt{q} - \sqrt{\underline{r}}\right)\right]. \label{eq:chi-square-sufficient-2}
\end{align}
By our choice of $q$ in \eqref{eq:choice-of-q}, the last probability in \eqref{eq:chi-square-sufficient-2} can be bounded from above by 
\begin{align*}
    \P\Big[Z_\nu < -\sqrt{2(1-\beta)\log{p}}\Big]
    &\sim \frac{\phi\left(-\sqrt{2(1-\beta)\log{p}}\right)}{\sqrt{2(1-\beta)\log{p}}} \\
    &= \frac{1}{\sqrt{2(1-\beta)\log{p}}}p^{-(1-\beta)},
\end{align*}
where the first line uses Mill's ratio for Gaussian distributions (see Section \ref{sec:Gaussian} and Relation \eqref{eq:Mills-ratio}).
This, combined with \eqref{eq:chi-square-sufficient-1}, completes the proof of the sufficient condition for the Bonferroni's procedure.

@@

Meanwhile, for any $i\in S$, by Lemma \ref{lemma:stochastic-monotonicity} and the fact that signal sizes are bounded above by $\overline{\Delta}$, we have,
\begin{equation*}
    {\chi_\nu^2(\lambda(i))} \stackrel{\mathrm{d}}{\le}
    {\chi_\nu^2(\overline{\Delta})} \stackrel{\mathrm{d}}{=} 
    {Z_1^2 + \ldots + Z_{\nu-1}^2 + \left(Z_\nu + \sqrt{\overline{\Delta}}\right)^2}.
\end{equation*}
Dividing through by $u_p$, and taking minimum over $S$, we obtain
\begin{equation} \label{eq:chi-square-necessary-3}
    \frac{m_S}{u_p} 
    = \min_{i\in S} \frac{\chi_\nu^2(\lambda(i))}{u_p} 
    % \stackrel{\mathrm{d}}{\le} \min \left\{\frac{\chi_\nu^2(\overline{\Delta})}{u_p}, s \text{ iid copies} \right\} \\
    \stackrel{\mathrm{d}}{\le} 
    \min_{i\in S}\left\{\frac{Z_1^2(i) + \ldots + Z_{\nu-1}^2(i)}{u_p} + \frac{(Z_\nu(i) + \sqrt{\overline{\Delta}})^2}{u_p}\right\}.
\end{equation}
Let $i^\dagger = i^\dagger_p$ be the index minimizing the second term in \eqref{eq:chi-square-necessary-3}, i.e.,
\begin{equation}
    i^\dagger := \argmin_{i\in S} \frac{(Z_\nu(i) + \sqrt{\overline{\Delta}})^2}{u_p}
    = \argmin_{i\in S} f_p\left(Z_\nu(i)\right),
    % \frac{(Z_\nu(i) + \sqrt{\overline{\Delta}})^2}{2\log{p}},
\end{equation}
where $f_p(x):=(x+\sqrt{\overline{\Delta}})^2/(2\log{p})$. 
We shall first show that 
\begin{equation} \label{eq:chi-square-necessary-4}
    %\min_{i\in S} \frac{(Z_\nu(i) + \sqrt{\overline{\Delta}})^2}{2\log{p}} 
    \P[ f_p(Z_\nu(i^\dagger)) < 1 -\delta ] \to 1,
\end{equation}
for some small $\delta>0$.
On the one hand, we know (by solving a quadratic inequality) that
\begin{equation} \label{eq:chi-square-necessary-5}
    f_p(x)<1-\delta \iff \frac{x}{\sqrt{2\log{p}}} \in (-(\sqrt{\overline{r}}+\sqrt{1-\delta}), -(\sqrt{\overline{r}}-\sqrt{1-\delta})).
\end{equation}
On the other hand, we know (by the relative stability of iid Gaussians, recall Section \ref{sec:Gaussian}) that 
\begin{equation} \label{eq:chi-square-necessary-6}
    % f_p(\min_{i\in S}z_\nu(i)) =
    \frac{\min_{i\in S} Z_\nu(i)}{\sqrt{2\log{p}}}
    \to -\sqrt{1-\beta} \quad\text{in probability}.
\end{equation}
Further, by the assumption on the signal sizes $\overline{r} < (1+\sqrt{1-\beta})^2$, we have,
\begin{equation*}
    -(\sqrt{\overline{r}}+1) < -1 <- \sqrt{1-\beta} < - (\sqrt{\overline{r}}-1).
\end{equation*}
Therefore we can picking a small $\delta>0$ such that 
\begin{equation} \label{eq:chi-square-necessary-7}
    -(\sqrt{\overline{r}}+1) < -(\sqrt{\overline{r}}+\sqrt{1-\delta})
    < - \sqrt{1-\beta}
    < - (\sqrt{\overline{r}}-\sqrt{1-\delta})
    < - (\sqrt{\overline{r}}-1).
\end{equation}
Combining \eqref{eq:chi-square-necessary-5}, \eqref{eq:chi-square-necessary-6}, and \eqref{eq:chi-square-necessary-7}, we obtain
\begin{align*}
    \P\left[\min_{i\in S} f_p(Z_\nu(i)) < 1-\delta\right]
    &= \P\left[ f_p(Z_\nu(i^\dagger)) < 1-\delta \right] \\
    &\ge \P\left[ f_p\left(\min_{i\in S}Z_\nu(i)\right) < 1-\delta \right] \to 1,
\end{align*}
and we arrive at \eqref{eq:chi-square-necessary-4}.
As a corollary, since $u_p\sim2\log{p}$, it follows that
\begin{equation} \label{eq:chi-square-necessary-8}
    \P\left[\min_{i\in S}\frac{(Z_\nu(i) + \sqrt{\overline{\Delta}})^2}{u_p} < 1-\delta\right]\to1.
\end{equation}

@@

The proof follows the ideas in \cite{arias2017distribution}, and is very similar to the proof of Theorem \ref{thm:Gaussian-error-approx-boundary}. 
One could in principle obtain the proofs in this section by referencing arguments that have appeared in Chapter \ref{chap:phase-transitions}.
We choose to present the proof here in full to make this section self-contained.

@@

As with the proof of Theorem \ref{thm:chi-squared-approx-boundary}, one could shorten the presentations in this section by 
referencing arguments in Chapter \ref{chap:phase-transitions}.  Again, we choose to present the proof in full to make this section 
self-contained.
